### 2024-07-10 Article/Article-english.tex
more

>>>>

\section*{5. Linear independence over an~abelian group}

In~any abelian group $G$ there is naturally defined multiplication by~integers.
For a~vector $\alpha = (\alpha_1, \ldots, \alpha_k) \in \mathbb{Z}^k$ and~element $g \in G$
by~$g \alpha$ we mean the~vector $(\alpha_1 g, \ldots, \alpha_k g) \in G^k$. We say that
the~collection of~vectors $\alpha_1, \ldots, \alpha_n \in \mathbb{Z}^k$ is \textit{linearly independent
over an~abelian group} if
$$
    \forall g_1, \ldots, g_n \in G{:}\ g_1 \alpha_1 + \ldots + g_n \alpha_n = 0 \Rightarrow g_1 = \ldots = g_n = 0.
$$

We see that the~linear independence of~vectors from $\mathbb{Z}^k$ over the~additive group of~the~field $\mathbb{R}$
is equivalent to~the~ordinary linear independence in~the~vector space $\mathbb{R}^k$. However, for example,
$\mathbb{R} / 2 \pi \mathbb{Z}$, as it is known, has no ring structure, so it makes no sense
to~talk about the~$\mathbb{R} / 2 \pi \mathbb{Z}$-module $(\mathbb{R} / 2 \pi \mathbb{Z})^k$,
as well as about linear independence in it.

Let us immediately show how this definition is related to~the~studied parameterizations $\phi_\alpha$.

\medskip\noindent\textbf{Theorem~6.}\emph{
    $\phi_\alpha : G^k \rightarrow G^n$ is injective if and only if $\alpha^j$ are linearly independent over the~group $G$.
}\medskip

\noindent{\it Proof.} It follows directly from the~fact that injectivity of~a~homomorphism is equivalent to the~triviality of~its kernel.
\hfill$\Box$\medskip

Next, we need two general lemmas.

\medskip\noindent\textbf{Lemma~8.}\emph{
    Let $G$ and~$H$ be abelian groups. $\mu_1,\allowbreak \ldots,\allowbreak \mu_n \in \mathbb{Z}^k$ are linearly independent
    over~$G \times H$ if and only if the are linearly independent over~$G$ and~over~$H$.
}\medskip

\noindent{\it Proof.}
    The~elements of~$G \times H$ can be expressed as pairs $(g, h)$ where $g \in G$ and~$h \in H$,
    so linear independence over~$G \times H$ can be written as:
    $$
        \forall (g_1, h_1) \ldots, (g_n, h_n) \in G \times H{:}\ (g_1, h_1) \mu_1 + \ldots + (g_n, h_n) \mu_n = 0 \Rightarrow (g_1, h_1) = \ldots = (g_n, h_n) = 0.
    $$
    Furthermore, it is clear that
    $$
        (g_1, h_1) \mu_1 + \ldots + (g_n, h_n) \mu_n = 0 \Leftrightarrow g_1 \mu_1 + \ldots + g_n \mu_n = 0 \wedge h_1 \mu_1 + \ldots + h_n \mu_n = 0,
    $$
    as well as
    $$
        (g_1, h_1) = \ldots = (g_n, h_n) = 0 \Leftrightarrow g_1 = \ldots = g_n = 0 \wedge h_1 = \ldots = h_n = 0.
    $$

    By~fixing $g_1 = \ldots = g_n = 0$ and~then $h_1 = \ldots = h_n = 0$, we'll obtain the~left-to-right
    implication. The~right-to-left implication is obvious.
\hfill$\Box$\medskip

\medskip\noindent\textbf{Lemma~9.}\emph{
    Let $G$ and~$H$ be abelian groups, $f : G \rightarrow H$ be an~isomorphism. Then $\mu_1, \ldots, \mu_n \in \mathbb{Z}^k$
    are linearly independent over~$G$ if and only if they are linearly independent over~$H$.
}\medskip

\noindent{\it Proof.}
    Since $f$ is an~isomorphic, we obtain a~chain of~equivalences:
    \begin{align*}
                       &\ \forall g_1, \ldots, g_n \in G{:}\ g_1 \alpha_1 + \ldots + g_n \alpha_n = 0 \Rightarrow g_1 = \ldots = g_n = 0 \\
        \Leftrightarrow&\ \forall g_1, \ldots, g_n \in G{:}\ f(g_1 \alpha_1 + \ldots + g_n \alpha_n) = 0 \Rightarrow g_1 = \ldots = g_n = 0 \\
        \Leftrightarrow&\ \forall g_1, \ldots, g_n \in G{:}\ f(g_1) \alpha_1 + \ldots + f(g_n) \alpha_n = 0 \Rightarrow f(g_1) = \ldots = f(g_n) = 0 \\
        \Leftrightarrow&\ \forall h_1, \ldots, h_n \in H{:}\ h_1 \alpha_1 + \ldots + h_n \alpha_n = 0 \Rightarrow h_1 = \ldots = h_n = 0.
        \tag*{$\Box$}
    \end{align*}
{}

Applying the~lemmas, we obtain the~injectivity criterion for~the~case $K = \mathbb{C}$.

\medskip\noindent\textbf{Consequence.}\emph{
    $\phi_\alpha$ is injective if and only if $\alpha^j$ are linearly independent over the~groups $\mathbb{R}$ and~$\mathbb{R} / 2 \pi \mathbb{Z}$.
}\medskip
